Improving legitimacy and efficiency \\ of decisions in democratic communities

### 2017-09-19 statistical-quorum.tex
Cleaning the language about the survey.

Before the introduction of the application, community had a practice of meeting weekly, with all
members being invited to participate. For decision making it used variation of Robert's rules~\cite{roberts}
with majority and super-majority voting to adopt decisions, generally using hand voting and voice voting.
A fixed quorum of the third of the membership was used. Meetings generally lasted between one to three hours.
Public minutes were taken of those meetings.

We introduced the application in fall 2016 semester for 16 weeks. We use spring 2016 as a baseline for comparison,
16 weeks as well, when traditional decision making was used.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/survey-comparison.pdf}
\caption{Results of a survey at the end of spring and fall semesters about general perception of the decision making in the house.
For each question, a participant was asked to rank on a scale between 1 (completely disagree) and 7 (completely agree). All members
of the community were invited to participate in the survey.}
\label{fig:survey-comparison}
\end{figure}

>>>>

Before the introduction of the application, community had a practice of weekly meetings, councils, with all
members being invited to participate. For decision making it used variation of Robert's rules~\cite{roberts}
with majority and super-majority voting to adopt decisions, generally using hand voting and voice voting.
A fixed quorum of $30\%$ of the membership was used (42 members). Councils generally lasted between one to three hours.
Public minutes were taken.

We introduced the application in fall 2016 semester which lasted 16 weeks. We use spring 2016 semester as
a baseline for comparison, which lasted 16 weeks as well and traditional decision making was used.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{figures/survey-comparison.pdf}
\caption{Results of a survey at the end of spring and fall semesters about general perception of the decision making (councils) in the community.
For each question, a participant was asked to rank on a scale between 1 (completely disagree) and 7 (completely agree). All members
of the community were invited to participate in the survey.}
\label{fig:survey-comparison}
\end{figure}
